Look, we can do something

### 2024-11-14 paper.tex
Add citations

In the following algorithms we will use a notion of single linked lists (or
simply lists). A list of elements of type \texttt{a} can be defined using the
following data type with two constructors, \texttt{[]} and \texttt{(:)}:
\begin{verbatim}
data List a = [] | a:(List a)
\end{verbatim}
The first constructor creates an empty list and the second attaches an element
of type \texttt{a} to the list of elements of type \texttt{a}. Sometimes we will
use conventional functions for working with lists such as \texttt{head},
\texttt{tail}, \texttt{map}, \texttt{foldl} and so on.

@@

The first flaw can be dealt with by replacing the Euclidean distance $\rho_{AB}$
in \cref{eq:intro} with the length $d_{AB}$ of the shortest path between points
which does not cross the pore's boundary (see \cref{fig:improved}). Although the
resulting algorithm will have the same $O(n^2)$ complexity, doing so can
increase computational time significantly. We call the parameter $P'$ with
$d_{AB}$ in the place of $\rho_{AB}$ ``improved narrowness''. The following
relation always holds: $0 < P \le P' \le 1$.
\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth,frame]{images/improved.png}
  \caption[]{Pairs of points responsible for narrowness (red) and improved
    narrowness (green).}
  \label{fig:improved}
\end{figure}

>>>>

In the following algorithms we will use a notion of single linked lists (or
simply lists). A list of elements of type \texttt{a} can be defined using the
following data type with two constructors, \texttt{[]} and \texttt{(:)}:
\begin{verbatim}
data List a = [] | a:(List a)
\end{verbatim}
The first constructor creates an empty list and the second attaches an element
of type \texttt{a} to the list of elements of type \texttt{a}. Sometimes we will
use conventional functions for working with lists such as \texttt{head},
\texttt{tail}, \texttt{map}, \texttt{foldl} and so on\cite[Chapter~4: Functional
programming]{o2008real}.

@@

The first flaw can be dealt with by replacing the Euclidean distance $\rho_{AB}$
in \cref{eq:intro} with the length $d_{AB}$ of the shortest path between points
which does not cross the pore's boundary (see \cref{fig:improved}). We can treat
the boundary as a simple polygon and there is a fast $O(n)$ algorithm for
finding the shortest path between points inside such
polygon\cite{guibas1986linear} once its triangulation is known. One of the
simplest triangulation algorithms is ear clipping
algorithm\cite{eberly2008triangulation} which works in $O(n^2)$ time. Other
works on the shortest path problem include
\cite{asano2010constant,har2014shortest,cleve2019experimental,asano1985visibility}.
Although the resulting algorithm will have the same $O(n^2)$ complexity, doing
so can increase computational time significantly. We call the parameter $P'$ with
$d_{AB}$ in the place of $\rho_{AB}$ ``improved narrowness''. The following
relation always holds: $0 < P \le P' \le 1$.
\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth,frame]{images/improved.png}
  \caption[]{Pairs of points responsible for narrowness (red) and improved
    narrowness (green).}
  \label{fig:improved}
\end{figure}
